abc

### 2024-07-07 randpython.qmd
okay

1.

```{webr-r}
fit = lm(mpg ~ am, data = mtcars)
summary(fit)
```

>>>>

```{webr-r}
webr::install(c("dplyr","purrr"))
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
library(dplyr)
library(ManifoldDestinyWASMP)
ls("package:dplyr")
ls("package:ManifoldDestinyWASMP")
data(package="ManifoldDestinyWASMD")
```

```{webr-r}
fit = lm(mpg ~ am, data = mtcars)
summary(fit)

```
